Bioverse: Origins of Life

### 2024-06-20 src/tex/ms.tex
explain Bioverse

\subsection{Exoplanet survey simulations with Bioverse}
To model the sensitivity of the information gain of a proposed mission to sample selection and survey strategy, we now conduct survey simulations with Bioverse using different sample sizes and survey strategies.
We again require that life occurs only on planets with sufficient past UV irradiation exceeding $F_\mathrm{NUV, min}$.
Further, we require this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}.

>>>>

\subsection{Exoplanet survey simulations with Bioverse}
To assess the information gain of a real exoplanet survey, we employed Bioverse~\citep{Bixel2021}, a framework that integrates multiple components including statistically realistic simulations of exoplanet populations, a survey simulation module, and a Bayesian hypothesis testing module to evaluate the statistical power of different observational strategies.
The general approach is as follows:
\begin{enumerate}
%    \item We simulate a synthetic population of exoplanets with known properties, including their host stars, orbital parameters, and physical characteristics.
\item \textbf{Exoplanet population synthesis:} We populate the Gaia Nearby Star Catalog with synthetic exoplanets whose orbital parameters and planetary properties reflect our current understanding of exoplanet demographics.
    \item \textbf{Survey Simulation:} We simulate the detection and characterization of these exoplanets with a hypothetical survey, taking into account the survey's sensitivity, target selection, and observational biases.
    \item \textbf{Hypothesis Tests:} We employ Bayesian statistical methods to evaluate the likelihood that a given survey would detect a specified statistical trend in the exoplanet population and estimate the precision with which the survey could constrain the parameters of that trend.
\end{enumerate}
To model the sensitivity of the information gain of a proposed mission to sample selection and survey strategy, we conduct survey simulations with Bioverse using different sample sizes and survey strategies.

To test the UV hypothesis, we require that life occurs only on planets with sufficient past UV irradiation exceeding $F_\mathrm{NUV, min}$.
Further, we require this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}.
